\large A new global measure of environmental unpredictability

### 2025-04-04 writing/appendix-1.Rmd
re-shuffled figures and added Okabe & Ito ref

\noindent The figures below illustrate some of the data used for fitting the models. All color palettes below are available via the `khroma` package [@frerebeau_khroma_2024] for `R` [@r_core_team_r_2024]. The code for generating the figures is available [on GitHub](https://github.com/QuantitativeEcologyLab/ndvi-stochasticity/blob/main/analysis/figures/input-data.R). The figure below illustrates each color palette for each type of vision (trichromatic, deuteranope, protanope, tritanope, and achomatic). Palette A is commonly attributed to Masataka Okabe and Kei Ito [@ichihara_color_2008], while the other palettes were created by Fabio Crameri [@crameri_geodynamic_2018; @crameri_scientific_2018].

>>>>

\noindent The figures below illustrate some of the data used for fitting the models. All color palettes below are available via the `khroma` package [@frerebeau_khroma_2024] for `R` [@r_core_team_r_2024]. The code for generating the figures is available [on GitHub](https://github.com/QuantitativeEcologyLab/ndvi-stochasticity/blob/main/analysis/figures/input-data.R). The figure below illustrates each color palette for each type of vision (trichromatic, deuteranope, protanope, tritanope, and achomatic). Palette A was created by Masataka Okabe and Kei Ito [@okabe_color_2008], while the other palettes were created by Fabio Crameri [@crameri_geodynamic_2018; @crameri_scientific_2018].
